---
title: "hackathon_1.2"
author: "Daniel Boppert"
date: "2023-12-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(ggplot2)
library(tidyverse)
library(scales)
library(sjlabelled)
```

```{r}
survey <- readRDS('survey/meof_usa_survey_df.RDS')
survey <- haven::as_factor(survey)
tracking <- readRDS('tracking/meof_usa_web_df.RDS')

```
Write a function that lets you illustrate the distribution of answers for a given discrete
choice question (not: questions with open text) on each of the survey waves. The
function should:

• take the data frame and survey item as arguments.
• return a small multiple barplot grouped at the survey wave-level with the answer
option counts (including Nas as a separate category).
• present the original survey question (label) and the variable name in the title of the
plot, and the data source in a footnote below the plot.
• graph the value labels in the answer tick axis (i.e., in presvote16post, you would
want “Hillary Clinton”, “Donald Trump”, etc., rather than the numbers
representing these values).
• have an additional argument that lets the user determine whether absolute
numbers (counts) or relative shares (in % of respondents) are reported.
• stop if the input variable is not a labelled <dbl+lbl> type.

Prove the correct behavior of the function with at least three survey questions,
highlighting that the arguments work as intended on (and only on) valid variable
types.

```{r}

library(dplyr)
library(ggplot2)
library(rlang)
library(forcats)

library(dplyr)
library(ggplot2)

create_facet_plot <- function(survey_data, var_name, relative = FALSE) {
  # Check if the variable is of type 'labelled' and 'double'
  if (!inherits(survey_data[[var_name]], c("labelled", "double"))) {
    stop("The variable is not of type 'labelled <dbl+lbl>'. Function will stop.")
  }
  variable_label <- get_label(survey_data[[var_name]])

  # Retrieving question label and data source from survey_data attributes
  data_source <- "Data Source: Guess, Andrew M.; Barberá, Pablo; Yang, JungHwan; Munzert, Simon (2022): Media
  Exposure and Opinion Formation in an Age of Information Overload (MEOF) – Survey U.S.A..
  GESIS Data Archive, Cologne. ZA7895 Data file Version 1.0.0, doi:10.4232/1.13980"

  # Convert NA to a factor level named "Missing"
  survey_data[[var_name]] <- haven::as_factor(survey_data[[var_name]])
  survey_data[[var_name]][is.na(survey_data[[var_name]])] <- "Missing"

  # Group by wave and var_name, and calculate counts
  grouped_data <- survey_data %>%
    group_by(wave, .data[[var_name]]) %>%
    summarise(count = n(), .groups = 'drop')

  # Determine the plot title based on relative or absolute counts
  count_type <- if(relative) "in Relative Counts" else "in Absolute Counts"
  plot_title <- paste(variable_label, "(", var_name, ") -", count_type)

  if (relative) {
    # Calculate percentages and create the plot with percentages
    grouped_data <- grouped_data %>%
      group_by(wave) %>%
      mutate(percentage = count / sum(count) * 100) %>%
      ungroup()

    plot <- ggplot(grouped_data, aes(x = .data[[var_name]], y = percentage, fill = wave)) +
      geom_bar(stat = "identity") +
      geom_text(aes(label = sprintf("%.1f%%", percentage)), vjust = -0.5, size = 3) +
      facet_grid(~wave) +
      theme_minimal() +
      theme(plot.caption = element_text(hjust = 0, size = 8)) + # Adjust caption text size here
      labs(title = plot_title, 
           y = "Percentage (%)", 
           x = "",
           caption = data_source) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            plot.caption = element_text(hjust = 0))
  } else {
    # Create the plot with absolute counts and add labels
    plot <- ggplot(grouped_data, aes(x = .data[[var_name]], y = count, fill = wave)) +
      geom_bar(stat = "identity") +
      geom_text(aes(label = count), vjust = -0.5, size = 3) +
      facet_grid(~wave) +
      theme_minimal() +
      theme(plot.caption = element_text(hjust = 0, size = 8)) + # Adjust caption text size here
      labs(title = plot_title, 
           y = "Count", 
           x = "",
           caption = data_source) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1),
            plot.caption = element_text(hjust = 0))
  }

  return(plot)
}

create_facet_plot(survey, "presvote16post", relative = FALSE)






```




















