---
title: "hackathon_1.2"
author: "Daniel Boppert"
date: "2023-12-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(ggplot2)
library(tidyverse)
```

```{r}
survey <- as_factor(readRDS('survey/meof_usa_survey_df.RDS'))
tracking <- readRDS('tracking/meof_usa_web_df.RDS')

```
Write a function that lets you illustrate the distribution of answers for a given discrete
choice question (not: questions with open text) on each of the survey waves. The
function should:

• take the data frame and survey item as arguments.
• return a small multiple barplot grouped at the survey wave-level with the answer
option counts (including Nas as a separate category).
• present the original survey question (label) and the variable name in the title of the
plot, and the data source in a footnote below the plot.
• graph the value labels in the answer tick axis (i.e., in presvote16post, you would
want “Hillary Clinton”, “Donald Trump”, etc., rather than the numbers
representing these values).
• have an additional argument that lets the user determine whether absolute
numbers (counts) or relative shares (in % of respondents) are reported.
• stop if the input variable is not a labelled <dbl+lbl> type.

Prove the correct behavior of the function with at least three survey questions,
highlighting that the arguments work as intended on (and only on) valid variable
types.

```{r}


plot_data <- survey %>%
    group_by(wave, pid7) %>%
    mutate(count = n()) %>% 
    ungroup() %>%
    select(wave, pid7,count) %>%
    unique()

ggplot(plot_data, aes(x = pid7, y = count, fil = wave)) +
         geom_bar()








party_lean <- function(survey_data, survey_question, relative = FALSE) {
  
  plot_data <- survey_data %>%
    group_by(survey_data$wave, survey_question) %>%
    mutate(count = n()) %>%
    ungroup()
  
   if (relative) {
    plot_data <- plot_data %>%
      group_by(wave) %>%
      mutate(relative_count = count / sum(count) * 100) %>%
      ungroup()
   }
  
  count_type <- if (relative) "relative_count" else "count"
  
  party_lean_plot <- ggplot(plot_data, aes(x = survey_question, y = count, fill = wave)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    labs(title = paste("Survey Question:", survey_question),
         x = "Answer Options",
         y = ifelse(relative, "Percentage (%)", "Counts"),
         caption = "Data source") +
    facet_wrap(~ wave) 
  
  return(party_lean_plot)
}  
  

party_lean(survey, pid7, relative = TRUE)








```




















